\documentclass[a4paper,12pt]{article}
\usepackage[left=1in,right=1in,top=0.9in,bottom=0.9in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{fontawesome}
%% \usepackage{tcolorbox}
%% \usepackage{tikz}

% Set the font to Arial
\usepackage{fontspec}
\setmainfont{Lato}[Scale=1.0]

% Define custom colors
\definecolor{darkblue}{RGB}{0,0,139}
\definecolor{gray}{RGB}{128,128,128}

% Customize section headings
\titleformat{\section}{\Large\bfseries\color{black}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0em}{2em}{0.8em}

\linespread{1.3}
\hyphenpenalty=10000
\exhyphenpenalty=10000

\setlength{\parindent}{0pt}  % Remove first-line indent

% Define a command for the main resume entries
\newcommand{\resumeentry}[2]{
    \textbf{#1} \\
    \textit{#2}
}

\pagestyle{empty} % Disable page numbering

\begin{document}
\begin{minipage}[t][2.4cm]{\textwidth}
    \raggedright
    {\Huge\bfseries\color{black}Dr. Atiya Fyruz} \\
    \large{BMDC Reg. No - 126871}
\end{minipage}
\begin{minipage}[t][17cm]{\textwidth}
  \section*{Profile}
	Dynamic medical professional with a comprehensive educational background and impactful internship at Sir Salimullah Medical College \& Mitford Hospital. 
	Conducted patient assessments, actively contributed to treatment plans, and proficiently executed diverse medical procedures under supervision. 
	Seeking to leverage academic and practical experience in a dynamic healthcare environment.
	\\
\section*{Experience}
	\resumeentry{Internship}{October, 2022 - September, 2023}\\ Sir Salimullah Medical College \& Mitford Hospital \vspace{0.2cm}
\begin{itemize}[left=0em, topsep=0pt, itemsep=4pt, parsep=0pt]
	\item Provided comprehensive treatment to patients on both inpatient and outpatient bases, demonstrating versatility in delivering healthcare across varied settings.
	\item Actively participated in 1200+ patient assessments, including history-taking, physical examinations, and the timely ordering of diagnostic tests.
  \item Collaborated closely with a multidisciplinary medical team, actively engaging in daily rounds and contributing to treatment plans for 300+ patients during the internship.
  \item Performed medical procedures, including wound dressings (50+), wound closure (10+), catheterization (10+), NG tube insertion (20+), paracentesis (5+), blood transfusion (100+), chemotherapy (5+) under direct supervision, consistently adhering to established medical standards and safety protocols.
	\item Provided daily follow-ups to patients, ensuring ongoing monitoring and adjustment of treatment plans for optimal recovery.
	\item Engaged in continuous and personalized communication with patients, effectively conveying treatment plans, preventive healthcare measures, and post-discharge care instructions to over 500 individuals. Demonstrated strong communication skills by providing ongoing counseling to both patients and their attendants throughout their healthcare experience.
	\item Applied strong documentation skills by writing order sheets for patients, preoperative and postoperative orders, death certificates, and maintaining the admission register.
\end{itemize}
\end{minipage}
\newpage
\begin{minipage}[t][7.4cm]{\textwidth}
\raggedright
\section*{Education}
\resumeentry{MBBS}{January, 2017 - May, 2022}\\ Sir Salimullah Medical College \vspace{0.2cm} \\ 
\textbf{HSC}, \textit{2016}\\ Holy Cross College, Dhaka \vspace{0.2cm} \\
\textbf{SSC}, \textit{2014}\\ Mohammadpur Preparatory High School, Dhaka \\
\end{minipage}
\begin{minipage}[t][8cm]{0.45\textwidth}
\section*{Skills}
\begin{itemize}[left=0em, itemsep=0pt, parsep=0pt]
  \item Emergency management
	\item Medical Proficiency
	\item Patient Assessment
	\item Multidisciplinary Collaboration
	\item Medical Procedures
	\item Patient Follow-up
	\item Effective Communication
	\item Documentation Proficiency
\end{itemize}
\end{minipage}
\hspace{0.5cm}\hspace{0.5cm}
\begin{minipage}[t][8cm]{0.45\textwidth}
\section*{Contact}
    \begin{minipage}[t]{0.1\textwidth}
        \faPhone\\
        \faMapMarker\\
        \faEnvelopeO
        %\faLinkedin
    \end{minipage}
    \begin{minipage}[t]{0.7\textwidth}
        01782 400 884\\
        Dhanmondi, Dhaka\\
        atiyafyruz132@gmail.com
        %linkedin.com/in/yourprofile
    \end{minipage}
%\section*{References}
%Available upon request.
\end{minipage}
\\
\begin{minipage}[b][6cm]{0.3\textwidth}
\par\noindent\rule{\textwidth}{0.4pt}
\centering{Signature}
\end{minipage}
\end{document}
