\documentclass[a4paper,12pt]{article}
\usepackage[left=0.7in,right=0.7in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{fontspec}
\setmainfont{Liberation Sans}[Scale=1.0]

\linespread{1.3}
\setlength{\parindent}{0pt}  % Remove first-line indent
\hyphenpenalty=10000
\exhyphenpenalty=10000
\pagestyle{empty} % Disable page numbering

\begin{document}
Principal \\
Shaheed Monsur Ali Medical College \\
House 26 \& 26A, Road No 10A, \\
Sector 11, Uttara, Dhaka - 1230 \\ 
\\
Dear Sir, \vspace{5mm}
\\
I am writing to express my sincere interest in the Lecturer position at Shaheed Monsur Ali Medical College, as advertised. 
Enclosed is my resume, and I am eager to bring my skills and passion for medical education to contribute to the academic excellence 
of your esteemed institution. \vspace{5mm}
\\
I'm \textbf{Dr. Asadul Al Galib}, an MBBS graduate with a year of internship experience. My education at Sir Salimullah Medical College 
instilled in me a strong foundation in medical expertise and academic excellence, earning honors in various subjects and 
securing positions in the top 10 under the University of Dhaka in 1st, 3rd and Final Professional Examination. \vspace{5mm}
\\
During my internship at \textbf{Sir Salimullah Medical College}, I honed clinical skills, connecting theoretical knowledge 
to real-world scenarios crucial in medical education. During my tenure at \textbf{MedX}, I played a pivotal role as a Co-founder, 
leading operational strategies, bringing success to the startup. Conducting diverse educational initiatives, including 
free live classes, strategic exam sessions, and paid courses, showcased my comprehensive understanding of medical education intricacies. 
As a Lecturer at \textbf{Udvash - Unmesh Shikkha Poribar} since 2017, I demonstrated teaching proficiency, instructing high school and college students 
in Physics and Biology. Additionally, as a Lecturer at Science Private Program, I taught Biology to medical and varsity admission examinees, 
showcasing adaptability to diverse learners. \vspace{5mm}
\\
What excites me most about the prospect of joining Shaheed Monsur Ali Medical College is the opportunity to contribute 
to the institution's academic excellence and foster student growth. I am confident that my combination of medical expertise, 
teaching proficiency, and dedication aligns well with the values of your esteemed institution. \vspace{5mm}
\\
Thank you for considering my application. I am enthusiastic about the possibility of contributing to 
Shaheed Monsur Ali Medical College and would welcome the opportunity to discuss how my skills and experiences 
align with your institution's vision. I look forward to the chance for an interview. \\
\\
Sincerely, \\
Dr. Asadul Al Galib \\
BMDC Reg. No - 126870 \\ 
Mobile No: 01521-430992 \\
Email: dr.asadul.algalib@gmail.com
\end{document}
